CRUSE to Safe Cycling in Ireland \\\large{An Open Source Tool to Support Active Travel}

### 2023-10-03 paper.tex
12 changes from eugeni (#13)
* Update abstract

* Add aim

* Add section on routing

* Add route type section

* Add figures to illustrate fastest and quietest network types

* Figure caption

* Update with route network type figures

* Add stats

* Describe Near Market

* Add scenarios, close #12

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, interior hidden, enhanced, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

@@

The datasets outlined above were used to generate estimates of cycling
currently (the `Baseline' scenario) and under four scenarios of cycling
potential: Near Market, Climate Action Plan, Go Dutch, and Ebike. Each
of these scenarios is described below.

The Baseline scenario approximates current cycling levels. As outlined

Near market Climate Action Plan Go Dutch Ebike

>>>>

\begin{keyword}
    Cycling \sep Open-source \sep Road Safety \sep 
    Active Travel
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, interior hidden, breakable]}{\end{tcolorbox}}\fi

@@

These map are available on the `Route types' page for each county (see
\href{https://cruse.bike/limerick/route-types}{cruse.bike/limerick/route-types}).
In addition to showing the estimated routes under each scenario, the
page also presents summary statistics on the network:

\begin{itemize}
\item
  On the fastest network, 25\% of the distance cycled occurs in
  non-hostile segments and 6\% in cycle-friendly segments.
\item
  Under the baseline scenario, 55\% of the distance cycled on the
  quietest network occurs in non-hostile segments and 13\% in
  cycle-friendly segments.
\end{itemize}

These statistics can be revealing: in Limerick it suggests that around
half of all cycling activity occurs on network segments that are hostile
(with a high inferred level of traffic stress), even when efforts are
taken to avoid busy segments. For the Fastest network, which may be more
realistic for utility cycling, the proportion of cycling on hostile
segments is even higher at 75\%.

TODO: Add description of route types in Limerick based on local
knowledge and Figure~\ref{fig-route-types}.

@@

The datasets outlined above were used to generate estimates of cycling
currently (the `Baseline' scenario) and under four scenarios of cycling
potential: Near Market, Climate Action Plan, Go Dutch, and Ebike. Each
of these scenarios is described below, as illustrated in Figure
Figure~\ref{fig-scenarios}.

\includegraphics{images/paste-7.png}

\caption{\label{fig-scenarios}Distance-mode share graph for Limerick
used to communicate the different scenarios. Source: county level view
for Limerick in the open access CRUSE Tool at
\url{https://cruse.bike/limerick}.}

\hypertarget{baseline}{%
\subsubsection{Baseline}\label{baseline}}

The Baseline scenario approximates current cycling levels. As outlined
in Section~\ref{sec-trip-purposes}, the Baseline scenario includes
travel to work and school, and additional trip purposes. Cycling levels
were taken from the POWSCAR data, which includes the number of people
travelling by each mode between each OD pair.

\hypertarget{near-market}{%
\subsubsection{Near Market}\label{near-market}}

The Near Market scenario approximates the level of cycling that would be
achieved if levels of cycling uptake observed in areas of Ireland with
high levels of cycling according to the 2016 Census were achieved
everywhere, accounting for differences in trip distances and hilliness
levels. The scenario is implemented as follows:

\begin{itemize}
\tightlist
\item
  Calculate distance decay curves for Dublin for the base year (2016,
  using POWSCAR data) by fitting a model to the relevant OD data after
  it has been converted to a route network datasest
\item
  Apply the Near Market model to the hilliness and distance values for
  each county during the build process
\item
  Add the current level of cycling to the Near Market model
\end{itemize}

\hypertarget{climate-action-plan}{%
\subsubsection{Climate Action Plan}\label{climate-action-plan}}

The Climate Action Plan scenario is loosely based on the Irish
Government's
\href{https://www.gov.ie/en/publication/6223e-climate-action-plan-2021/}{Climate
Action Plan 2021}, which contains policies for action to achieve a 51\%
reduction in overall greenhouse gas emissions by 2030, on a path towards
net-zero by 2050. For transport, this includes 500,000 extra walking,
cycling and public transport trips per day by 2030. In terms of car
travel, the target is to ``Increas{[}e{]} the proportion of kilometres
driven by passenger electric cars to between 40 and 45\% by 2030, in
addition to a reduction of 10\% in kilometres driven by the remaining
internal combustion engine cars.'' This equates to a 5.5 to 6\%
reduction in total car km driven.

To model this decrease in car driver km, cycling uptake increases in
line with the Go Dutch scenario. However, we only model shift from
driving to cycling. There is no shift from other modes of transport to
cycling.

\hypertarget{go-dutch}{%
\subsubsection{Go Dutch}\label{go-dutch}}

Under the Go Dutch scenario cycling reaches levels equivalent to those
found in the Netherlands, taking account of the effects of route
hilliness (measured as mean gradient) and route distance. This scenario
uses the same model that was used PCT, allowing trips to shift from any
other mode to cycling \citep{lovelace2017}.

\hypertarget{ebike}{%
\subsection{Ebike}\label{ebike}}

Also based on the PCT scenario with the same name, the Eike scenario in
CRUSE takes Go Dutch cycling uptake, and adds onto this the impact of
increased ebike usage, which allows for longer cycle trips. However,
travel to primary and secondary schools still uses Go Dutch uptake,
since no ebike scenario has been developed for school journeys, and
children may be less likely to own ebikes than adults.
